Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-06-10 constantRate/ConstCompFuzzExt.tex
Adding info-theoretic construction and reusability

\newcommand{\expinfo}{\ensuremath{\mathcal{E}}}
\newcommand{\ext}{\ensuremath{\mathtt{ext}}}
\newcommand{\cext}{\ensuremath{\mathtt{cext}}}
\newcommand{\rext}{\ensuremath{\mathtt{rext}}}
\newcommand{\cons}{\ensuremath{\mathtt{cons}}}
\newcommand{\decons}{\ensuremath{\mathtt{decons}}}

@@

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for point functions with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.  When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
\section{Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

@@

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together  .  We use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
%The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.  %In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  
We use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).  Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.  Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.  For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.

@@

There are two primary questions about the reusability of a fuzzy extractor.  The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.  Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.  Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.  In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.  However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.

@@

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.

@@

The next two sections are dedicated to proving this theorem.
 For security we argue that each of the $v_i$ values is unguessable.  For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.  For reusability, we show that \bnote{what?}

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then security follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{Reusability of \consref{cons:sampling}}
\bnote{write this}

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.

@@

>>>>

\newcommand{\expinfo}{\ensuremath{\mathcal{E}}}
\newcommand{\ext}{\ensuremath{\mathtt{ext}}}
\newcommand{\cext}{\ensuremath{\mathtt{cext}}}
\newcommand{\cond}{\ensuremath{\mathtt{cond}}}
\newcommand{\rext}{\ensuremath{\mathtt{rext}}}
\newcommand{\cons}{\ensuremath{\mathtt{cons}}}
\newcommand{\decons}{\ensuremath{\mathtt{decons}}}

@@

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.  When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
\section{Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

@@

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together  .  We use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
%The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.  %In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  
We use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).  Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.  Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.  For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.

@@

There are two primary questions about the reusability of a fuzzy extractor.  The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.  Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.  Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They show in the setting of unbounded reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.  In particular, they show how any information-theoretic fuzzy extractor secure with unbounded reuse can be transformed into their construction.  However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.

@@

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}

@@

The next two sections are dedicated to proving this theorem.
 For security we argue that each of the $v_i$ values is unguessable.  For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.  Reusability comes essentially for free given a sufficiently composable obfuscation for digital lockers.  For the sake of clarity we state reusability as a separate theorem~(\thref{thm:reusability}).

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then security follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} essentially follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator must still be able to simulate.  Thus, given sufficiently strong reusability we achieve the following stronger result:

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  Then \consref{cons:sampling} is $q$-reusable.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
\end{proof}

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

@@

\section{An information-theoretic construction with $\Huse\le 0$}
In this section we show an information-theoretic analogue to \consref{cons:first construction}.  %This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.  
Using this weaker object requires us to make a stronger assumption on our starting distribution.  Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.  Achieving these benefits information-theoretically is an open question.  We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).

The main idea of this construction is to first condense entropy from each block of the source and then apply a standard secure sketch to the extracted information.  Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.  %Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
We first review some information-theoretic definitions.

\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\begin{definition}
\label{def:conductor}
A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
\end{definition}

Note that randomness condensers can be built significantly more efficiently than randomness extractors~(see for example~\cite{dodis2013key}).

\begin{definition}
\label{def:fuzzy conductor}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
\begin{itemize}
\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.  That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
\end{itemize}
\end{definition}

\begin{lemma}
Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.  Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
\item Set $p = (ss, seed_1,..., seed_\ell)$.
\item Output $(v, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $v = \rec(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{lemma}
\begin{proof}
Let $W\in \mathcal{W}$.
It suffices to argue correctness and security.  We first argue correctness.  
When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.  Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.  Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.

We now argue security.  Denote by $seed$ the random variable consisting of all $\ell$ seeds and $V$ the entire string of generated $V_1,..., V_\ell$.
Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.  We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\ell)\approx (Y, seed_1,.., seed_\ell)$.  First note since $W$ is $(\alpha, \beta)$-partial block distribution that
there exists a set of indices $J$ where $|J| \geq \ell - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$, 
\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]

%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
%Then since $W$ is a block-source, 
%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
\noindent 
Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that 
\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
and since $(seed_1,..., seed_{j_1})$ are independent of these values
\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
Applying a deterministic function does not increase statistical distance and thus,
\begin{align*}
(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\epsilon} (Z_{j_1}, seed_{j_1},..., seed_1)
\end{align*}

\noindent
By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\ell -\beta)$ where 
\[
(\cond(W_\ell, seed_\ell), ..., \cond(W_1, seed_1), seed_\ell,..., seed_1) \approx_{\epsilon\ell} (Z, seed_\ell,...,  seed_1).\]
By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.  %Note that $U_{\mathcal{Y}}^\ell$ is independent of $seed_1,..., seed_\ell$ and so $\Hav(U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p)\ge \tilde{m}$. 
That is, 
\[
(V, seed_1,..., seed_\ell, p) \approx_{\epsilon\ell} (U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p).\]  This completes the proof.
\end{proof}
